### 2017-09-30 Graduate - Introduction to Analysis I/Assignment 4/4-homework20170925.tex
add Problem 6

@@

\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\bigskip

>>>>

\textbf{Solution:}
\textbf{(1)} Necessity: From $\{f_n\}$ converges to $f$ in measure and the property of convergence, we know that each subsequence of $\{f_n\}$ converges to $f$ in measure. From Problem 5(b) we know $\{f_{n_k}\}$ has a subsequence $\{f_{n_{k_{j}}}\}$ converges pointwise a.e. on $X$ to $f$.

Sufficiency: If each subsequence $\{f_{n_k}\}$ has a further subsequence $\{f_{n_{k_j}}\}$ converges pointwise a.e. on $X$ to $f$, then since $\mu(X) < \infty$, from Problem 5(a) we know $\{f_{n_k}\}$ converges in measure to $f$. If $\{f_n\}$ does not converge to $f$ in measure, then there $\exists \epsilon > 0$,
$$
\begin{aligned}
&\text{for}~ n_1 = 1, ~\exists n_2 > n_1, ~\mu(\{x\mid |f_{n_2}-f| \ge \epsilon\}) \ge \epsilon, \\
&\text{for}~ n_2, ~\exists n_3 > n_2, ~\mu(\{x\mid |f_{n_3}-f| \ge \epsilon\}) \ge \epsilon, \\
&\cdots, \\
&\text{for}~ n_k, ~\exists n_{k+1} > n_k, ~\mu(\{x\mid |f_{n_{k+1}}-f| \ge \epsilon\}) \ge \epsilon, \\
&\cdots.
\end{aligned}
$$
Then we get a subsequence $\{f_{n_k}\}$ which does not converge to $f$ in measure. It makes a contratiction.

\textbf{(2)} Suppose $\{f_n\}$, $\{g_n\}$ are two sequences that converge in measure to respectively $f$ and $g$. For each subsequence $\{f_{n_k}g_{n_k}\}$ of $\{f_ng_n\}$, from (1) we know $\{f_{n_k}\}$ has a subsequence $\{f_{n_{k_l}}\}$ converges pointwise a.e. to $f$, and $\{g_{n_{k_l}}\}$ has a subsequence $\{g_{n_{k_{l_j}}}\}$ converges pointwise a.e. to $g$. Since the union of two measure-zero sets is a measure-zero set, we know $\{f_{n_{k_{l_j}}}g_{n_{k_{l_j}}}\}$ converges pointwise a.e. to $fg$ according to the linear property of limits. Thus according to (1) we know $\{f_ng_n\}$ converges in measure to the product of limits.
\bigskip

@@

\textbf{Solution:}
